Dependent Object Types

### 2012-08-09 article.tex
ack tiark
move why no inheritance sec to discussion
outline / contrib

\subsection{Why No Inheritance?}

In the calculus we made the deliberate choice not to model any form of
inheritance. This is, first and foremost, to keep the calculus simple.
Secondly, there are many different approaches to inheritance and
mixin composition, so that it looks advantageous not to tie the basic
calculus to a specific one. Finally, it seems that the modelization of
inheritance lends itself to a different approach than the basic
calculus. For the latter, we need to prove type safety of the calculus.
One might try to do this also for a calculus with inheritance, but our
experience suggests that this complicates the proofs considerably.  An
alternative approach that might work better is to model inheritance
it as a form of code-reuse. Starting with an enriched type system with
inheritance, and a translation to the basic calculus, one needs to
show type safety wrt the translation. This might be easier than
to prove type safety wrt reduction.

\section{The DOT Calculus}

@@

@@

We thank Amal Ahmed for many discussions and insights about applying
logical relations to DOT. We thank Donna Malayeri and Geoffrey
Washburn for preliminary work on DOT.

>>>>

We propose DOT as a core calculus for path-dependent types. We present
the calculus formally in section \ref{pres} and through examples in
section~\ref{dot-examples}. Though we show that the calculus does not
satisfy the standard theorem of preservation in
section~\ref{dot-preservation}, we contribute a proof sketch of type
safety using logical relations in section~\ref{dot-type-safety}. In
section~\ref{discussion}, we discuss choices and variants of the
calculus, as well as related work, and conclude in
section~\ref{conclusion}.

\section{The DOT Calculus}\label{pres}

@@

\subsection{Why No Inheritance?}\label{why-no-inheritance}

In the calculus we made the deliberate choice not to model any form of
inheritance. This is, first and foremost, to keep the calculus simple.
Secondly, there are many different approaches to inheritance and
mixin composition, so that it looks advantageous not to tie the basic
calculus to a specific one. Finally, it seems that the modelization of
inheritance lends itself to a different approach than the basic
calculus. For the latter, we need to prove type safety of the calculus.
One might try to do this also for a calculus with inheritance, but our
experience suggests that this complicates the proofs considerably.  An
alternative approach that might work better is to model inheritance
as a form of code-reuse. Starting with an enriched type system with
inheritance, and a translation to the basic calculus, one needs to
show type safety wrt the translation. This might be easier than
to prove type safety wrt reduction.

@@

We thank Amal Ahmed for many discussions and insights about applying
logical relations to DOT. We thank Donna Malayeri and Geoffrey
Washburn for preliminary work on DOT. We thank Tiark Rompf for helpful
comments.
